Evaluating Regularization

### 2019-03-28 Scripts/evaluating_feature_reduction.Rmd
added enet results for k562

>>>>

#None
##OC
enetcoefs_none_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/ENET/enetModel.rds")
enetcoefs_none_oc_10kb_K562 <- coef(enetcoefs_none_oc_10kb_K562$finalModel, s=enetcoefs_none_oc_10kb_K562$bestTune$lambda)
##OP
enetcoefs_none_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/ENET/enetModel.rds")
enetcoefs_none_op_10kb_K562 <- coef(enetcoefs_none_op_10kb_K562$finalModel, s=enetcoefs_none_op_10kb_K562$bestTune$lambda)
##Distance
enetcoefs_none_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/ENET/enetModel.rds")
enetcoefs_none_dist_10kb_K562 <- coef(enetcoefs_none_dist_10kb_K562$finalModel, s=enetcoefs_none_dist_10kb_K562$bestTune$lambda)

#RUS
##OC
enetcoefs_RUS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OC/ENET/enetModel.rds")
enetcoefs_RUS_oc_10kb_K562 <- coef(enetcoefs_RUS_oc_10kb_K562$finalModel, s=enetcoefs_RUS_oc_10kb_K562$bestTune$lambda)
##OP
enetcoefs_RUS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/OP/ENET/enetModel.rds")
enetcoefs_RUS_op_10kb_K562 <- coef(enetcoefs_RUS_op_10kb_K562$finalModel, s=enetcoefs_RUS_op_10kb_K562$bestTune$lambda)
##Distance
enetcoefs_RUS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
enetcoefs_RUS_dist_10kb_K562 <- coef(enetcoefs_RUS_dist_10kb_K562$finalModel, s=enetcoefs_RUS_dist_10kb_K562$bestTune$lambda)

#ROS
##OC
enetcoefs_ROS_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OC/ENET/enetModel.rds")
enetcoefs_ROS_oc_10kb_K562 <- coef(enetcoefs_ROS_oc_10kb_K562$finalModel, s=enetcoefs_ROS_oc_10kb_K562$bestTune$lambda)
##OP
enetcoefs_ROS_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/OP/ENET/enetModel.rds")
enetcoefs_ROS_op_10kb_K562 <- coef(enetcoefs_ROS_op_10kb_K562$finalModel, s=enetcoefs_ROS_op_10kb_K562$bestTune$lambda)
##Distance
enetcoefs_ROS_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
enetcoefs_ROS_dist_10kb_K562 <- coef(enetcoefs_ROS_dist_10kb_K562$finalModel, s=enetcoefs_ROS_dist_10kb_K562$bestTune$lambda)

#SMOTE
##OC
enetcoefs_SMOTE_oc_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
enetcoefs_SMOTE_oc_10kb_K562 <- coef(enetcoefs_SMOTE_oc_10kb_K562$finalModel, s=enetcoefs_SMOTE_oc_10kb_K562$bestTune$lambda)
##OP
enetcoefs_SMOTE_op_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
enetcoefs_SMOTE_op_10kb_K562 <- coef(enetcoefs_SMOTE_op_10kb_K562$finalModel, s=enetcoefs_SMOTE_op_10kb_K562$bestTune$lambda)
##Distance
enetcoefs_SMOTE_dist_10kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
enetcoefs_SMOTE_dist_10kb_K562 <- coef(enetcoefs_SMOTE_dist_10kb_K562$finalModel, s=enetcoefs_SMOTE_dist_10kb_K562$bestTune$lambda)

enetcoefsmat <- cbind(enetcoefs_none_oc_10kb_K562[-1,1], 
                      enetcoefs_ROS_oc_10kb_K562[-1,1],
                      enetcoefs_RUS_oc_10kb_K562[-1,1], 
                      enetcoefs_SMOTE_oc_10kb_K562[-1,1],

                      enetcoefs_none_op_10kb_K562[-1,1], 
                      enetcoefs_ROS_op_10kb_K562[-1,1],
                      enetcoefs_RUS_op_10kb_K562[-1,1], 
                      enetcoefs_SMOTE_op_10kb_K562[-1,1],

                      enetcoefs_none_dist_10kb_K562[-1,1],
                      enetcoefs_ROS_dist_10kb_K562[-1,1],
                      enetcoefs_RUS_dist_10kb_K562[-1,1],
                      enetcoefs_SMOTE_dist_10kb_K562[-1,1])

#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
rownames(enetcoefsmat) <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "K562", 
                                                    "dist",
                                                    "count",
                                                    "perc",
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))

#None
##OC
enetcoefs_none_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/ENET/enetModel.rds")
enetcoefs_none_oc_25kb_K562 <- coef(enetcoefs_none_oc_25kb_K562$finalModel, s=enetcoefs_none_oc_25kb_K562$bestTune$lambda)
##OP
enetcoefs_none_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/ENET/enetModel.rds")
enetcoefs_none_op_25kb_K562 <- coef(enetcoefs_none_op_25kb_K562$finalModel, s=enetcoefs_none_op_25kb_K562$bestTune$lambda)
##Distance
enetcoefs_none_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/ENET/enetModel.rds")
enetcoefs_none_dist_25kb_K562 <- coef(enetcoefs_none_dist_25kb_K562$finalModel, s=enetcoefs_none_dist_25kb_K562$bestTune$lambda)

#RUS
##OC
enetcoefs_RUS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OC/ENET/enetModel.rds")
enetcoefs_RUS_oc_25kb_K562 <- coef(enetcoefs_RUS_oc_25kb_K562$finalModel, s=enetcoefs_RUS_oc_25kb_K562$bestTune$lambda)
##OP
enetcoefs_RUS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/OP/ENET/enetModel.rds")
enetcoefs_RUS_op_25kb_K562 <- coef(enetcoefs_RUS_op_25kb_K562$finalModel, s=enetcoefs_RUS_op_25kb_K562$bestTune$lambda)
##Distance
enetcoefs_RUS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
enetcoefs_RUS_dist_25kb_K562 <- coef(enetcoefs_RUS_dist_25kb_K562$finalModel, s=enetcoefs_RUS_dist_25kb_K562$bestTune$lambda)

#ROS
##OC
enetcoefs_ROS_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OC/ENET/enetModel.rds")
enetcoefs_ROS_oc_25kb_K562 <- coef(enetcoefs_ROS_oc_25kb_K562$finalModel, s=enetcoefs_ROS_oc_25kb_K562$bestTune$lambda)
##OP
enetcoefs_ROS_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/OP/ENET/enetModel.rds")
enetcoefs_ROS_op_25kb_K562 <- coef(enetcoefs_ROS_op_25kb_K562$finalModel, s=enetcoefs_ROS_op_25kb_K562$bestTune$lambda)
##Distance
enetcoefs_ROS_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
enetcoefs_ROS_dist_25kb_K562 <- coef(enetcoefs_ROS_dist_25kb_K562$finalModel, s=enetcoefs_ROS_dist_25kb_K562$bestTune$lambda)

#SMOTE
##OC
enetcoefs_SMOTE_oc_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
enetcoefs_SMOTE_oc_25kb_K562 <- coef(enetcoefs_SMOTE_oc_25kb_K562$finalModel, s=enetcoefs_SMOTE_oc_25kb_K562$bestTune$lambda)
##OP
enetcoefs_SMOTE_op_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
enetcoefs_SMOTE_op_25kb_K562 <- coef(enetcoefs_SMOTE_op_25kb_K562$finalModel, s=enetcoefs_SMOTE_op_25kb_K562$bestTune$lambda)
##Distance
enetcoefs_SMOTE_dist_25kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
enetcoefs_SMOTE_dist_25kb_K562 <- coef(enetcoefs_SMOTE_dist_25kb_K562$finalModel, s=enetcoefs_SMOTE_dist_25kb_K562$bestTune$lambda)

enetcoefsmat <- cbind(enetcoefs_none_oc_25kb_K562[-1,1], 
                      enetcoefs_ROS_oc_25kb_K562[-1,1],
                      enetcoefs_RUS_oc_25kb_K562[-1,1], 
                      enetcoefs_SMOTE_oc_25kb_K562[-1,1],

                      enetcoefs_none_op_25kb_K562[-1,1], 
                      enetcoefs_ROS_op_25kb_K562[-1,1],
                      enetcoefs_RUS_op_25kb_K562[-1,1], 
                      enetcoefs_SMOTE_op_25kb_K562[-1,1],

                      enetcoefs_none_dist_25kb_K562[-1,1],
                      enetcoefs_ROS_dist_25kb_K562[-1,1],
                      enetcoefs_RUS_dist_25kb_K562[-1,1],
                      enetcoefs_SMOTE_dist_25kb_K562[-1,1])

#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
rownames(enetcoefsmat) <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "K562", 
                                                    "dist",
                                                    "count",
                                                    "perc",
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))

#None
##OC
enetcoefs_none_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OC/ENET/enetModel.rds")
enetcoefs_none_oc_50kb_K562 <- coef(enetcoefs_none_oc_50kb_K562$finalModel, s=enetcoefs_none_oc_50kb_K562$bestTune$lambda)
##OP
enetcoefs_none_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/OP/ENET/enetModel.rds")
enetcoefs_none_op_50kb_K562 <- coef(enetcoefs_none_op_50kb_K562$finalModel, s=enetcoefs_none_op_50kb_K562$bestTune$lambda)
##Distance
enetcoefs_none_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/ENET/enetModel.rds")
enetcoefs_none_dist_50kb_K562 <- coef(enetcoefs_none_dist_50kb_K562$finalModel, s=enetcoefs_none_dist_50kb_K562$bestTune$lambda)

#RUS
##OC
enetcoefs_RUS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OC/ENET/enetModel.rds")
enetcoefs_RUS_oc_50kb_K562 <- coef(enetcoefs_RUS_oc_50kb_K562$finalModel, s=enetcoefs_RUS_oc_50kb_K562$bestTune$lambda)
##OP
enetcoefs_RUS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/OP/ENET/enetModel.rds")
enetcoefs_RUS_op_50kb_K562 <- coef(enetcoefs_RUS_op_50kb_K562$finalModel, s=enetcoefs_RUS_op_50kb_K562$bestTune$lambda)
##Distance
enetcoefs_RUS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
enetcoefs_RUS_dist_50kb_K562 <- coef(enetcoefs_RUS_dist_50kb_K562$finalModel, s=enetcoefs_RUS_dist_50kb_K562$bestTune$lambda)

#ROS
##OC
enetcoefs_ROS_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OC/ENET/enetModel.rds")
enetcoefs_ROS_oc_50kb_K562 <- coef(enetcoefs_ROS_oc_50kb_K562$finalModel, s=enetcoefs_ROS_oc_50kb_K562$bestTune$lambda)
##OP
enetcoefs_ROS_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/OP/ENET/enetModel.rds")
enetcoefs_ROS_op_50kb_K562 <- coef(enetcoefs_ROS_op_50kb_K562$finalModel, s=enetcoefs_ROS_op_50kb_K562$bestTune$lambda)
##Distance
enetcoefs_ROS_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
enetcoefs_ROS_dist_50kb_K562 <- coef(enetcoefs_ROS_dist_50kb_K562$finalModel, s=enetcoefs_ROS_dist_50kb_K562$bestTune$lambda)

#SMOTE
##OC
enetcoefs_SMOTE_oc_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
enetcoefs_SMOTE_oc_50kb_K562 <- coef(enetcoefs_SMOTE_oc_50kb_K562$finalModel, s=enetcoefs_SMOTE_oc_50kb_K562$bestTune$lambda)
##OP
enetcoefs_SMOTE_op_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
enetcoefs_SMOTE_op_50kb_K562 <- coef(enetcoefs_SMOTE_op_50kb_K562$finalModel, s=enetcoefs_SMOTE_op_50kb_K562$bestTune$lambda)
##Distance
enetcoefs_SMOTE_dist_50kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
enetcoefs_SMOTE_dist_50kb_K562 <- coef(enetcoefs_SMOTE_dist_50kb_K562$finalModel, s=enetcoefs_SMOTE_dist_50kb_K562$bestTune$lambda)

enetcoefsmat <- cbind(enetcoefs_none_oc_50kb_K562[-1,1], 
                      enetcoefs_ROS_oc_50kb_K562[-1,1],
                      enetcoefs_RUS_oc_50kb_K562[-1,1], 
                      enetcoefs_SMOTE_oc_50kb_K562[-1,1],

                      enetcoefs_none_op_50kb_K562[-1,1], 
                      enetcoefs_ROS_op_50kb_K562[-1,1],
                      enetcoefs_RUS_op_50kb_K562[-1,1], 
                      enetcoefs_SMOTE_op_50kb_K562[-1,1],

                      enetcoefs_none_dist_50kb_K562[-1,1],
                      enetcoefs_ROS_dist_50kb_K562[-1,1],
                      enetcoefs_RUS_dist_50kb_K562[-1,1],
                      enetcoefs_SMOTE_dist_50kb_K562[-1,1])

#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
rownames(enetcoefsmat) <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "K562", 
                                                    "dist",
                                                    "count",
                                                    "perc",
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))

#None
##OC
enetcoefs_none_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OC/ENET/enetModel.rds")
enetcoefs_none_oc_100kb_K562 <- coef(enetcoefs_none_oc_100kb_K562$finalModel, s=enetcoefs_none_oc_100kb_K562$bestTune$lambda)
##OP
enetcoefs_none_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/OP/ENET/enetModel.rds")
enetcoefs_none_op_100kb_K562 <- coef(enetcoefs_none_op_100kb_K562$finalModel, s=enetcoefs_none_op_100kb_K562$bestTune$lambda)
##Distance
enetcoefs_none_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/ENET/enetModel.rds")
enetcoefs_none_dist_100kb_K562 <- coef(enetcoefs_none_dist_100kb_K562$finalModel, s=enetcoefs_none_dist_100kb_K562$bestTune$lambda)

#RUS
##OC
enetcoefs_RUS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OC/ENET/enetModel.rds")
enetcoefs_RUS_oc_100kb_K562 <- coef(enetcoefs_RUS_oc_100kb_K562$finalModel, s=enetcoefs_RUS_oc_100kb_K562$bestTune$lambda)
##OP
enetcoefs_RUS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/OP/ENET/enetModel.rds")
enetcoefs_RUS_op_100kb_K562 <- coef(enetcoefs_RUS_op_100kb_K562$finalModel, s=enetcoefs_RUS_op_100kb_K562$bestTune$lambda)
##Distance
enetcoefs_RUS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/ENET/enetModel.rds")
enetcoefs_RUS_dist_100kb_K562 <- coef(enetcoefs_RUS_dist_100kb_K562$finalModel, s=enetcoefs_RUS_dist_100kb_K562$bestTune$lambda)

#ROS
##OC
enetcoefs_ROS_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OC/ENET/enetModel.rds")
enetcoefs_ROS_oc_100kb_K562 <- coef(enetcoefs_ROS_oc_100kb_K562$finalModel, s=enetcoefs_ROS_oc_100kb_K562$bestTune$lambda)
##OP
enetcoefs_ROS_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/OP/ENET/enetModel.rds")
enetcoefs_ROS_op_100kb_K562 <- coef(enetcoefs_ROS_op_100kb_K562$finalModel, s=enetcoefs_ROS_op_100kb_K562$bestTune$lambda)
##Distance
enetcoefs_ROS_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/ENET/enetModel.rds")
enetcoefs_ROS_dist_100kb_K562 <- coef(enetcoefs_ROS_dist_100kb_K562$finalModel, s=enetcoefs_ROS_dist_100kb_K562$bestTune$lambda)

#SMOTE
##OC
enetcoefs_SMOTE_oc_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OC/ENET/enetModel.rds")
enetcoefs_SMOTE_oc_100kb_K562 <- coef(enetcoefs_SMOTE_oc_100kb_K562$finalModel, s=enetcoefs_SMOTE_oc_100kb_K562$bestTune$lambda)
##OP
enetcoefs_SMOTE_op_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/OP/ENET/enetModel.rds")
enetcoefs_SMOTE_op_100kb_K562 <- coef(enetcoefs_SMOTE_op_100kb_K562$finalModel, s=enetcoefs_SMOTE_op_100kb_K562$bestTune$lambda)
##Distance
enetcoefs_SMOTE_dist_100kb_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/ENET/enetModel.rds")
enetcoefs_SMOTE_dist_100kb_K562 <- coef(enetcoefs_SMOTE_dist_100kb_K562$finalModel, s=enetcoefs_SMOTE_dist_100kb_K562$bestTune$lambda)

enetcoefsmat <- cbind(enetcoefs_none_oc_100kb_K562[-1,1], 
                      enetcoefs_ROS_oc_100kb_K562[-1,1],
                      enetcoefs_RUS_oc_100kb_K562[-1,1], 
                      enetcoefs_SMOTE_oc_100kb_K562[-1,1],

                      enetcoefs_none_op_100kb_K562[-1,1], 
                      enetcoefs_ROS_op_100kb_K562[-1,1],
                      enetcoefs_RUS_op_100kb_K562[-1,1], 
                      enetcoefs_SMOTE_op_100kb_K562[-1,1],

                      enetcoefs_none_dist_100kb_K562[-1,1],
                      enetcoefs_ROS_dist_100kb_K562[-1,1],
                      enetcoefs_RUS_dist_100kb_K562[-1,1],
                      enetcoefs_SMOTE_dist_100kb_K562[-1,1])

#colnames(enetcoefsmat) <- c(paste(c("OC","OP","Distance"), rep("None", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("RUS", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("ROS", 3), sep=" "),
#paste(c("OC","OP","Distance"), rep("SMOTE", 3), sep=" "))
colnames(enetcoefsmat) <- rep(c("None", "ROS", "RUS", "SMOTE"), 3)
rownames(enetcoefsmat) <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "K562", 
                                                    "dist",
                                                    "count",
                                                    "perc",
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", rownames(enetcoefsmat))
